### 2019-02-01 thesis_report/results.tex
Changed QC image

% -*- root: ./report.tex -*-
\chapter{Results \& Discussion}
		In this chapter, we show how the properties of the system change under introduction of the zigzag geometry.
		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in the Methods chapter.

@@

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.95\columnwidth]{figures/quasiclassical_approximation}
			\caption{Comparison of the topological gap computed using a full zigzag system implemented in Kwant with the quasiclassical estimate. The ratio $4\dfrac{z_x}{z_y}$ is kept constant at three different values, and the gap is calculated for varying $z_y$.
			The full lines represent  the numerical gap calculations of the full zigzag system, the dashed lines represent the quasiclassical estimation.}
			\label{fig:quasiclassical_approximation}
			\end{figure}

>>>>

% -*- root: ./report.tex -*-
\chapter{Results \& Discussion}\label{chap:results}
		In this chapter, we show how some properties of the system change by introduction of the zigzag geometry.
		Additionally, we attempt to isolate the mechanism behind the improved properties by estimating the gap size through the quasiclassical model introduced in chapter \ref{chap:methods}.

@@

			\begin{figure}[!htb]
			\centering
			\includegraphics[width=0.95\columnwidth]{figures/z_y_vs_E_gap}
			\caption{Comparison of the topological gap computed using a full zigzag system implemented in Kwant with the quasiclassical estimate. The ratio $4\dfrac{z_x}{z_y}$ is kept constant at three different values, and the gap is calculated for varying $z_y$.
			The full lines represent  the numerical gap calculations of the full zigzag system, the dashed lines represent the quasiclassical estimation.}
			\label{fig:quasiclassical_approximation}
			\end{figure}
